---
title: "click_frequency_with_position_normalize"
author: "Eva Zhong"
date: "May 3, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages}
library(dplyr)
library(caret)
library(caTools)
library(lme4)
```


```{r read data}
raw_df <- read.csv('rec_viewed_binary_5_03.csv')
str(raw_df)
```

```{r}
levels(raw_df$isViewed)[levels(raw_df$isViewed)=="True"] <- "TRUE"
levels(raw_df$isViewed)[levels(raw_df$isViewed)=="False"] <- "FALSE"

fields <- c('Algorithm','userId_x','SeedMovie','loginId','movieId','sessionIds','position_x','avgRating','popularityLastYear','avgRating_seedmovie','popularityLastYear_seedmovie','ageMonth','age_seedmovie_month','isViewed')
```

```{r}
rec_viewed <- raw_df[,fields]
colnames(rec_viewed)[colnames(rec_viewed)=="ageMonth"] <- "age_month"
```

```{r}
rec_viewed_nobaseline = filter(rec_viewed, Algorithm != 'ShuffledTopPicks')
rec_viewed_nobaseline$Algorithm = factor(rec_viewed_nobaseline$Algorithm, levels=c('PredictedRating','TagSimilarity','FilmReleaseDate'))

```

```{r remove bad data}
rec_viewed_small = filter(rec_viewed_nobaseline, age_seedmovie_month>=0)
rec_viewed_small = rec_viewed_small[complete.cases(rec_viewed_small),]
summary(rec_viewed_small)
```

## Normalize variables:
```{r}
rec_viewed_norm = rec_viewed_small[,c('Algorithm','userId_x','loginId','movieId','sessionIds','position_x','avgRating','popularityLastYear','avgRating_seedmovie','popularityLastYear_seedmovie','age_month','age_seedmovie_month','isViewed')]
```

```{r}
sd(rec_viewed_norm$age_seedmovie_month)
```

```{r normalize variables}
# Normalize by calculating mean and standard deviation
rec_viewed_norm$avgRating_seedmovie = (rec_viewed_norm$avgRating_seedmovie-3.599)/0.3937958
rec_viewed_norm$popularityLastYear_seedmovie = (rec_viewed_norm$popularityLastYear_seedmovie-669.6)/952.0824
rec_viewed_norm$age_seedmovie_month = (rec_viewed_norm$age_seedmovie_month-166.2)/169.7619
```
```{r}
summary(rec_viewed_norm)
```


## Training and testing set
```{r splitting training and testing set}
set.seed(123)   #  set seed to ensure you always have same random numbers generated
# set.seed(321)
sample = sample.split(rec_viewed_small,SplitRatio = 0.75) # splits the data in the ratio mentioned in SplitRatio. After splitting marks these rows as logical TRUE and the the remaining are marked as logical FALSE
train1 =subset(rec_viewed_small,sample ==TRUE) # creates a training dataset named train1 with rows which are marked as TRUE
test1=subset(rec_viewed_small, sample==FALSE)

# DO NOT CROSS VALIDATE. HUGE DATASET. 
```

```{r splitting training and testing set}
set.seed(123)   #  set seed to ensure you always have same random numbers generated
# set.seed(321)
sample = sample.split(rec_viewed_norm,SplitRatio = 0.75) # splits the data in the ratio mentioned in SplitRatio. After splitting marks these rows as logical TRUE and the the remaining are marked as logical FALSE
train1_1 =subset(rec_viewed_norm,sample ==TRUE) # creates a training dataset named train1 with rows which are marked as TRUE
test1_1=subset(rec_viewed_norm, sample==FALSE)

# DO NOT CROSS VALIDATE. HUGE DATASET. 
```


## Mixed effect model 2: Algs+Seed movie info
Train model on train1
```{r train model on train 1}
library(lme4)

# remove the effect of position
mixed_effect_logit2 <- glmer(isViewed ~ Algorithm+log(age_seedmovie_month+1)+avgRating_seedmovie+log(popularityLastYear_seedmovie + 1)+position_x+(1|userId_x), data = train1, family = binomial(link = "logit"), control = glmerControl(optimizer = 'bobyqa', optCtrl = list(maxfun=100000)))

# Set seed 123 results
summary(mixed_effect_logit2)
``` 

## Mixed effect model on training set 1_1, normalized
```{r}
mixed_effect_logit3_1 <- glmer(isViewed ~ Algorithm+age_seedmovie_month+avgRating_seedmovie+popularityLastYear_seedmovie + +position_x+(1|userId_x), data = train1_1, family = binomial(link = "logit"), control = glmerControl(optimizer = 'bobyqa', optCtrl = list(maxfun=100000)))
# Set seed 123 results
summary(mixed_effect_logit3_1) 
```

## Test (normalized) model on test1_1

```{r}
prob <- predict(mixed_effect_logit3_1, newdata=test1_1, type="response")
library(pROC)
roc_curve <- roc(test1_1$isViewed, prob)
auc(roc_curve)
```

run model on test1 (set seed 123)
```{r run model on test1}
mixed_effect_logit3 <- glmer(isViewed ~ Algorithm+log(age_seedmovie_month+1)+avgRating_seedmovie+log(popularityLastYear_seedmovie + 1)+position_x+(1|userId_x), data = test1, family = binomial(link = "logit"), control = glmerControl(optimizer = 'bobyqa', optCtrl = list(maxfun=100000)))
# Set seed 123 results
summary(mixed_effect_logit3) 

```

## Test mixed effect logistic Model by making prediction on test data:
```{r evaluate model}
prob <- predict(mixed_effect_logit2, newdata=test1, type="response")
library(pROC)
roc_curve <- roc(test1$isViewed, prob)
plot(roc_curve)
```
```{r}
auc(roc_curve)
```


# Compare the performance between Tagsimilarity and FilmReleaseDate
```{r}
rec_viewed_2 = subset(rec_viewed, Algorithm == 'TagSimilarity'|Algorithm =="FilmReleaseDate")
```

```{r remove bad data}
rec_viewed_small2 = filter(rec_viewed_2, age_seedmovie_month>=0)
rec_viewed_small2 = rec_viewed_small2[complete.cases(rec_viewed_small2),]
summary(rec_viewed_small2)
```

## Training and testing set
```{r splitting training and testing set}
set.seed(123)   #  set seed to ensure you always have same random numbers generated
# set.seed(321)
sample = sample.split(rec_viewed_small2,SplitRatio = 0.75) # splits the data in the ratio mentioned in SplitRatio. After splitting marks these rows as logical TRUE and the the remaining are marked as logical FALSE
train2 =subset(rec_viewed_small2,sample ==TRUE) # creates a training dataset named train1 with rows which are marked as TRUE
test2=subset(rec_viewed_small2, sample==FALSE)
# DO NOT CROSS VALIDATE. HUGE DATASET. 
```


## Mixed effect model 2: Algs+Seed movie info
Train model on train1
```{r train model on train 1}
library(lme4)

# Include the effect of position
mixed_effect_logit4 <- glmer(isViewed ~ Algorithm+log(age_seedmovie_month+1)+avgRating_seedmovie+log(popularityLastYear_seedmovie + 1)+position_x+(1|userId_x), data = train2, family = binomial(link = "logit"), control = glmerControl(optimizer = 'bobyqa', optCtrl = list(maxfun=100000)))

# Set seed 123 results
summary(mixed_effect_logit4)
``` 