---
title: "Statistical test - pairwise action frequency"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages}
library(dplyr)
library(caret)
library(caTools)
library(logistf)
library(lme4)
```


```{r}
# raw_df <- read.csv('rec_viewed_binary_3_30.csv')
raw_df <- read.csv('action_frequency_5_02.csv')
```

```{r}
str(raw_df)
```

```{r `}
#levels(raw_df$isViewed)[levels(raw_df$isViewed)=="True"] <- "TRUE"
#levels(raw_df$isViewed)[levels(raw_df$isViewed)=="False"] <- "FALSE"


fields <- c('recommenderId_x','userId_x','movieId','loginId','movieId','SeedMovie','sessionIds','avgRating','popularityLastYear','avgRating_seedmovie','popularityLastYear_seedmovie','age_month','age_seedmovie_month','isLiked','isDisliked','isWishlisted','viewedDetails')
```


```{r}
rec_viewed <- raw_df[,fields]
```


```{r}
colnames(rec_viewed)[colnames(rec_viewed)=="recommenderId_x"] <- "Algorithm"
```

## Preparing the dataset for pairwise comparison
```{r}
rec_viewed_small = filter(rec_viewed, age_seedmovie_month>=0)
rec_viewed_small = filter(rec_viewed_small, age_month>=0)
rec_viewed_small$Algorithm = factor(rec_viewed_small$Algorithm,levels=c("PredictedRating","TagSimilarity","FilmReleaseDate","ShuffledTopPicks"))

rec_viewed_small1 = subset(rec_viewed_small, Algorithm == 'PredictedRating' | Algorithm == 'TagSimilarity')
rec_viewed_small2 = subset(rec_viewed_small, Algorithm == 'PredictedRating' | Algorithm == 'FilmReleaseDate')
rec_viewed_small3 = subset(rec_viewed_small, Algorithm == 'FilmReleaseDate' | Algorithm == 'TagSimilarity')

# # rec_viewed_small = subset(rec_viewed_small, Algorithm == 'PredictedRating' | Algorithm == 'TagSimilarity')
#
```


```{r}
rec_viewed_small1 = rec_viewed_small1[complete.cases(rec_viewed_small1),]
rec_viewed_small2 = rec_viewed_small2[complete.cases(rec_viewed_small2),]
rec_viewed_small3 = rec_viewed_small3[complete.cases(rec_viewed_small3),]
```


## Wishlist: PredictedRating vs TagSimilarity
```{r PredictedRating vs TagSimilarity}
mixed_effect_logit_isWishlisted1 <- glmer(isWishlisted ~ Algorithm+(1|userId_x), data = rec_viewed_small1, family = binomial(link = "logit"), control = glmerControl(optimizer = 'bobyqa', optCtrl = list(maxfun=100000)) )
#+avgRating_seedmovie+log(popularityLastYear_seedmovie+1)+log(age_seedmovie_month+1)
summary(mixed_effect_logit_isWishlisted1)
fitted.results1 <- predict(mixed_effect_logit_isWishlisted1,type="response")
summary(fitted.results1)
```
## Wishlist: PredictedRating vs FilmReleaseDate
```{r PredictedRating vs FilmReleaseDate}
mixed_effect_logit_isWishlisted2 <- glmer(isWishlisted ~ Algorithm+(1|userId_x), data = rec_viewed_small2, family = binomial(link = "logit"), control = glmerControl(optimizer = 'bobyqa', optCtrl = list(maxfun=100000)) )
#avgRating_seedmovie+log(popularityLastYear_seedmovie+1)+log(age_seedmovie_month+1)
summary(mixed_effect_logit_isWishlisted2)
fitted.results2 <- predict(mixed_effect_logit_isWishlisted2,type="response")
summary(fitted.results2)
```
## Wishlist: TagSimilarity vs FilmReleaseDate
```{r TagSimilarity vs FilmReleaseDate}
mixed_effect_logit_isWishlisted3 <- glmer(isWishlisted ~ Algorithm+(1|userId_x), data = rec_viewed_small3, family = binomial(link = "logit"), control = glmerControl(optimizer = 'bobyqa', optCtrl = list(maxfun=100000)))
#+avgRating_seedmovie+log(popularityLastYear_seedmovie+1)+log(age_seedmovie_month+1)
summary(mixed_effect_logit_isWishlisted3)
fitted.results3 <- predict(mixed_effect_logit_isWishlisted3,type="response")
summary(fitted.results3)
```

## viewedDetails: PredictedRating vs TagSimilarity (not used in paper)
```{r}
mixed_effect_logit_viewedDetails1 <- glmer(viewedDetails ~ Algorithm+(1|userId_x), data = rec_viewed_small1, family = binomial(link = "logit"), control = glmerControl(optimizer = 'bobyqa', optCtrl = list(maxfun=100000)) )
#+avgRating_seedmovie+log(popularityLastYear_seedmovie+1)+log(age_seedmovie_month+1)
summary(mixed_effect_logit_viewedDetails1)
fitted.results1 <- predict(mixed_effect_logit_viewedDetails1,type="response")
summary(fitted.results1)
```
## viewedDetails: PredictedRating vs FilmReleaseDate (not used in paper)
```{r}
mixed_effect_logit_viewedDetails2 <- glmer(viewedDetails ~ Algorithm+(1|userId_x), data = rec_viewed_small2, family = binomial(link = "logit"), control = glmerControl(optimizer = 'bobyqa', optCtrl = list(maxfun=100000)) )
#avgRating_seedmovie+log(popularityLastYear_seedmovie+1)+log(age_seedmovie_month+1)
summary(mixed_effect_logit_viewedDetails2)
fitted.results2 <- predict(mixed_effect_logit_viewedDetails2,type="response")
summary(fitted.results2)
```
## viewedDetails: TagSimilarity vs FilmReleaseDate (not used in paper)
```{r}
mixed_effect_logit_viewedDetails3 <- glmer(viewedDetails ~ Algorithm+(1|userId_x), data = rec_viewed_small3, family = binomial(link = "logit"), control = glmerControl(optimizer = 'bobyqa', optCtrl = list(maxfun=100000)))
#+avgRating_seedmovie+log(popularityLastYear_seedmovie+1)+log(age_seedmovie_month+1)
summary(mixed_effect_logit_viewedDetails3)
fitted.results3 <- predict(mixed_effect_logit_viewedDetails3,type="response")
summary(fitted.results3)
```