---
title: "Trailer Analysis Statistical Test"
author: "Eva Zhong"
date: "April 2, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_packages}
library(dplyr)
library(caret)
library(caTools)
library(logistf)

```


```{r}
# raw_df <- read.csv('rec_viewed_binary_3_30.csv')
raw_df <- read.csv('rec_viewed_binary_4_02.csv')

```


```{r `}
levels(raw_df$isViewed)[levels(raw_df$isViewed)=="True"] <- "TRUE"
levels(raw_df$isViewed)[levels(raw_df$isViewed)=="False"] <- "FALSE"


fields <- c('Algorithm','userId_x','SeedMovie','loginId','movieId','sessionIds','avgRating','popularityLastYear','avgRating_seedmovie','popularityLastYear_seedmovie','age_month','age_seedmovie_month','isViewed')
```



```{r}
rec_viewed <- raw_df[,fields]
str(rec_viewed)
```

Reorder Algorithm factors:
```{r}
rec_viewed$Algorithm = factor(rec_viewed$Algorithm, levels = c("ShuffledTopPicks", "TagSimilarity", "FilmReleaseDate", "PredictedRating"), ordered = TRUE)
```

```{r}
rec_viewed_small = filter(rec_viewed, age_seedmovie_month>=0)
rec_viewed_small[complete.cases(rec_viewed_small),]
str(rec_viewed_small)

```

Quick Summary statistics:
```{r}
sd(log(rec_viewed_small$age_seedmovie_month+1))
sd(rec_viewed_small$avgRating)

```




```{r}
# TODO: 
# 1. Training set and testing set
# 2. Regular logistic model
# 3. Firth method logistic model  https://www.rdocumentation.org/packages/logistf/versions/1.22/topics/logistf
```


## Train the model and Test Result
Training set and testing set
```{r}
# set.seed(123)   #  set seed to ensure you always have same random numbers generated
# set.seed(321)
set.seed(500)
# set.seed(600)
sample = sample.split(rec_viewed_small,SplitRatio = 0.75) # splits the data in the ratio mentioned in SplitRatio. After splitting marks these rows as logical TRUE and the the remaining are marked as logical FALSE
train1 =subset(rec_viewed_small,sample ==TRUE) # creates a training dataset named train1 with rows which are marked as TRUE
test1=subset(rec_viewed_small, sample==FALSE)

# DO NOT CROSS VALIDATE. HUGE DATASET. 
```
```{r}
summary(test1)
```

## A basic logistic regression model 
```{r}
logistic_fit <- glm(formula = isViewed ~ Algorithm+avgRating_seedmovie+age_seedmovie_month+avgRating+age_month, data = test1, family = binomial)
```
```{r}
summary(logistic_fit)
```
```{r}
library(QuantPsyc)
lm.beta(logistic_fit)
```

Any correlation between FilmReleaseDate and age_month?
```{r}
# View(rec_viewed_small)
boxplot(avgRating ~ Algorithm, data = rec_viewed_small)
```

Strength of association between age_month and Algorithm:
```{r}
rec_viewed_small_frdfrd = filter(rec_viewed_small, Algorithm=="FilmReleaseDate")
```

```{r}
model.lm <- lm(avgRating ~ Algorithm, data = rec_viewed_small)
summary(model.lm)
# aov1 = aov(rec_viewed_small$age_month ~ rec_viewed_small$Algorithm)
# summary(aov1)
```

```{r}
ggplot(data = rec_viewed_small, mapping = aes(x = avgRating)) + 
  geom_freqpoly(mapping = aes(colour = Algorithm))
```



```{r mixed-effect model}
library(lme4)

mixed_effect_logit <- glmer(isViewed ~ Algorithm+avgRating_seedmovie+log(popularityLastYear_seedmovie+1)+log(age_seedmovie_month+1)+avgRating+log(popularityLastYear+1)+log(age_month+1)+(1|userId_x), data = train1, family = binomial(link = "logit"), control = glmerControl(optimizer = 'bobyqa', optCtrl = list(maxfun=100000)) )

summary(mixed_effect_logit)
```
```

A basic logistic regression model 
```{r}
logistic_train1 <- glm(formula = isViewed ~ Algorithm+avgRating_seedmovie+log(popularityLastYear_seedmovie+1)+log(age_seedmovie_month+1)+avgRating+log(popularityLastYear+1)+log(age_month+1), data = train1, family = binomial("logit"))

```

```{r}
summary(logistic_train1)
```

Test Model by making prediction on test data:

```{r}
prob = predict(logistic_train1, newdata = test1,type="response")
test1$prob = prob
library(pROC)

```

```{r}
levels(test1$isViewed)[levels(test1$isViewed)=="TRUE"] <- 1
levels(test1$isViewed)[levels(test1$isViewed)=="FALSE"] <- 0

```

Plotting ROC
```{r}
# Encode as 0 and 1
roc_curve <- roc(test1$isViewed, prob)
plot(roc_curve)
```

Calculating AUC:
```{r}
auc(roc_curve)
```


```{r}
logistic_prediction <- predict(logistic_train1, newdata = test1,type="response")
#confusionMatrix(data = logistic_prediction, reference = test1$isViewed)
logistic_prediction
```

```{r}
logistic_train1
levels(test1$isViewed)
accuracy <- table(logistic_prediction, test1$isViewed)
sum(diag(accuracy))/sum(accuracy)
```




<!-- Logit Model Penalized Likelihood -->
<!-- ```{r} -->
<!-- library(logistf) -->
<!-- firth_logit <- logistf(isViewed ~ Algorithm+avgRating_seedmovie+log(popularityLastYear_seedmovie+1)+log(age_seedmovie_month+1)+avgRating+log(popularityLastYear+1)+log(age_month+1), rec_viewed_small, firth=TRUE) -->
<!-- ``` -->


